### 2021-02-20 math/ia_2021/paper.tex
cleanup
update

@@

>>>>

\section{Statistical Model}

\subsection{Cleaning the dataset}

The dataset, \cite{noaa}

\subsection{Regression}

\subsection{Ease of access of data}
For an easy access to the predictions generated by the program, I implemented 
a simple function to fetch new earthquake events from the \url{https://earthquake.usgs.gov/earthquakes/feed/v1.0/geojson.php} 
live earthquake feed. These earthquake events are quantified into a magnitude \verb|mag| 
and a distance \verb|dist| variable, which are supplied to the statistical model. 
This information is then easily accessible from a human-readable report exported 
to a plaintext file.

\section{Uses of this research}

The research included in this paper could be useful for many life-saving scenarios, 
notably ones in which, for example, high quality and large-scale tsunami alert 
systems are not available.

\section{Conclusion}

\subsection{Evaluation of the method used}

This method, like any other statistical approximation, is by no means perfect 
and for that reason should not be used in any real-world application. The results 
procured by the program

@@

\appendix
\section{Appendix}
\label{app}
\subsection{Python program}
\label{app:scripts}
qsd
\lstinputlisting[language=Python]{model/multregr.py}
